---
title: "Aland_HW_4"
author: "Aland"
date: "2/23/2022"
output: html_document
---

```{r, include=FALSE}
library(palmerpenguins)
library(rstatix)
library(dplyr)
library(ggplot2)
```

##creating data for usage
```{r, echo=FALSE, include=FALSE}

Adelie_mass_given = penguins %>% 
  dplyr::filter(species=="Adelie") %>%
  select(body_mass_g)
  
 summary(Adelie_mass_given) 
 
 Adelie_given_max = 4775 

 Chinstrap_mass_given = penguins %>%
   dplyr::filter(species=="Chinstrap") %>%
   select(body_mass_g)
 
 summary(Chinstrap_mass_given) #adult male max 

 Chinstrap_given_max = 4800
 
 Adelie_mass_lit = 5000 #adult male max
 
 Chinstrap_mass_lit = 4453

 #Choinstrap_lit is 4453, given is 4800, both maxes
 #Adelie lit is 5000, given is 4775
 
 Chinstrap_masses= data.frame(Chinstrap_mass_given, Chinstrap_mass_lit)
 Adelie_masses= data.frame(Adelie_mass_given, Adelie_mass_lit)

```


```{r, echo=FALSE}
Adelie_comp_plot = ggplot() +
geom_histogram(data = Adelie_masses, aes(y=Adelie_masses$body_mass_g)) +
  geom_histogram(data = Adelie_masses, aes(y=Adelie_masses$Adelie_mass_lit, fill = Adelie_mass_lit))

Adelie_comp_plot

Chinstrap_comp_plot = ggplot() +
geom_histogram(data = Chinstrap_masses, aes(y=Chinstrap_masses$body_mass_g)) + 
geom_histogram(data = Chinstrap_masses, aes(y=Chinstrap_masses$Chinstrap_mass_lit, fill = Chinstrap_mass_lit))


Chinstrap_comp_plot
```


```{r}
t.test(Adelie_masses$body_mass_g, Adelie_masses$Adelie_mass_lit, var.equal=T)

```
Q.1 Adelie Mass Comparison

- After running an idependent two tailed t-test, the Adelie masses from the palmer dataset and the observed value from the literature are significantly different from each other. The two sample t test yielded a p value of 2.2e-16, which is FAR less than 0.05. 



```{r}

t.test(Chinstrap_masses$body_mass_g, Chinstrap_masses$Chinstrap_mass_lit, var.equal=T)


```

Q.2 Chinstrap

- After running an idependent two tailed t-test, the Chinstrap masses from the palmer dataset and the observed value from the literature are significantly different from each other. The two sample t test yielded a p value of 2.2e-16, which is FAR less than 0.05. 

```{r}

t.test(Chinstrap_masses$body_mass_g, Adelie_masses$body_mass_g, var.equal=T)


```

Q.3 

- After running an idependent two tailed t-test, the Chinstrap masses from the palmer dataset and the Adelie masses from the same dataset are not significantly different from each other. The two sample t test yielded a p value of 0.6119, which is much higher than than 0.05. 


```{r, echo=FALSE}
Penguin_combo = penguins %>% 
  dplyr::select(body_mass_g, flipper_length_mm)


Penguin_combo

ggplot() +
  geom_point(data = Penguin_combo, aes(x=Penguin_combo$body_mass_g, y=Penguin_combo$flipper_length_mm))


  
cor(x=Penguin_combo$body_mass_g, y=Penguin_combo$flipper_length_mm)

cor.test(x=Penguin_combo$body_mass_g, y=Penguin_combo$flipper_length_mm)

```
Q.4

- Comparison of the flipper length and body mass of all penguin species combined yielded interesting results. visually in the scatterplot, as body mass increased, flipper length appeared to increase on a linear pattern. When a Pearson's product-moment correlation test is run, the "cor" value comes out to a 0.871. This value is very strong, and suits the linear pattern fromt the scatterplot. 



```{r}

Adelie_set = penguins %>%
  filter(species=="Adelie") %>%
  select(body_mass_g, flipper_length_mm)

Chinstrap_set = penguins %>%
  filter(species=="Chinstrap") %>%
  select(body_mass_g, flipper_length_mm)

Gentoo_set = penguins %>%
  filter(species=="Gentoo") %>%
  select(body_mass_g, flipper_length_mm)

cor.test(x=Adelie_set$body_mass_g, y=Adelie_set$flipper_length_mm)

cor.test(x=Chinstrap_set$body_mass_g, y=Chinstrap_set$flipper_length_mm)

cor.test(x=Gentoo_set$body_mass_g, y=Gentoo_set$flipper_length_mm)


```
Q.5
- Pearson's product-moment correlation test was run on the relationship between flipper length and body mass for all 3 species of penguins. Adelie's had a cor value of 0.468, Chinstraps had a cor value of 0.641, and Gentoos had a cor value of 0.702. while all meaningful correlations, the Gentoo penguins exhinited the strongest correlation between the two factors. 
